Neural Networks Loss Landscape Convergence in Different Low-Dimensional Spaces

### 2025-03-20 paper/main.tex
Universal commits presents...

\begin{definition}
  Let $\Delta$ be a positive hyperparameter that indicates the stop-difference for $\Delta_k$. If
  $$k^* = \inf\limits_k\{\Delta_k < \Delta\}$$
  we can say that $k^*$ samples in the dataset are enough to describe the distribution of data from the general population.
  We call $k^*$ as \textbf{sufficient}.
\end{definition}

>>>>

\begin{definition}
  Let $\Delta$ be a positive hyperparameter that indicates the stop-difference for $\Delta_k$. If
  $$k^* = \inf\limits_k\{\forall m \geq k: \, \Delta_m < \Delta\}$$
  we can say that $k^*$ samples in the dataset are enough to describe the distribution of data from the general population.
  We call $k^*$ as \textbf{sufficient}.
\end{definition}
